Covariate analysis of UFL-Mayo-ISB RNASeq (both cerebellum and temporal cortex) samples from MayoBrainBank_Dickson alone

### 2016-05-16 code/Rmd/Mayo_MayoBrainBankDickson_RNASeq.Rmd
Minor sanity changes

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = RESIDUAL.GENE_EXPRESSION$ensembl_gene_id,
                       mart = mart)
RESIDUAL.GENE_EXPRESSION <- left_join(RESIDUAL.GENE_EXPRESSION, Ensemble2HGNC) %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=25, fig.width=25}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

>>>>

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = RESIDUAL.GENE_EXPRESSION$ensembl_gene_id,
                       mart = mart)
RESIDUAL.GENE_EXPRESSION <- left_join(RESIDUAL.GENE_EXPRESSION, Ensemble2HGNC) %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=16, fig.width=25}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
